Triplots and Output Elasticities

### 2015-09-17 Testing/Elasticity.Rmd
add comparision with different reindexing

@@

## Trajectories of Ouput Elasticities (2 examples)
```{r, plots, cache = FALSE}
bigData <-
  bind_rows(
    fortify(modUK) %>% mutate(Country = "UK"),
    fortify(modPT) %>% mutate(Country = "PT")
  )
model2OE(bigData) + facet_wrap( ~ Country)

```

>>>>

```{r}
UK2 <- 
  modUK$data %>%
  mutate(
    iGDP = iGDP / tail(iGDP, 1),
    iKservO.WwithRD = iKservO.WwithRD / tail(iKservO.WwithRD, 1),
    ihLest = ihLest / tail(ihLest, 1),
    iU = iU / tail(iU, 1)
  )

PT2 <- 
  modPT$data %>%
  mutate(
    iGDP = iGDP / tail(iGDP, 1),
    iKservS.L = iKservS.L / tail(iKservS.L, 1),
    ihLest = ihLest / tail(ihLest, 1),
    iUMP = iUMP / tail(iUMP, 1)
  )

modUK2 <- cesModel( iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, data = UK2)
modPT2 <- cesModel( iGDP ~ iKservS.L + ihLest + iUMP + iYear, data = PT2)
```

@@

## Trajectories of Ouput Elasticities (2 examples)
```{r, plots, cache = FALSE}
bigData <-
  bind_rows(
    fortify(modUK) %>% mutate(Country = "UK", reindex = "first"),
    fortify(modPT) %>% mutate(Country = "PT", reindex = "first"),
    fortify(modUK2) %>% mutate(Country = "UK", reindex = "last"),
    fortify(modPT2) %>% mutate(Country = "PT", reindex = "last")
  )
model2OE(bigData) + facet_grid(reindex ~ Country)
```
